---
title: "PracticalMachineLearning_Assignment.rmd"
output: html_document
---  
  
The objective of the exercise is to predict the activity class of physical exercises conducted by 6 participants.  

We will run the analysis on the following data  
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv  

We first load the data.  
```{r}
library(caret)
data <- read.csv("pml-training.csv")
```

Because activity class would be predicted only be the measurement, we decide to remove timestamp and username from the feature set.  
Also due to unavailability of data in some columns (avg, stddev, min, max, skewness and kurtosis) we also decide to remove from the feature set.  
```{r}
headers <- names(data)
non_predictors <- grep("X|user_name|timestamp|window|avg|stddev|var|min|max|skewness|kurtosis|amplitude", headers)
```


We can then create a training set and a testing set
```{r}
intrain <- createDataPartition(y=data$classe, p=0.7, list=FALSE)
training <- data[intrain,-non_predictors]
testing <- data[-intrain,-non_predictors]
```


We chose to run Random Forest for this exercise as the algorithm would provide best accuracy for this classification problem  
```{r, cache=TRUE}
modFit <- train(classe ~ ., data=training, method="rf")
```


Finaly we run the prediction model to the testing data and run cross-validation table to check the error
```{r}
prediction <- predict(modFit, testing)
table(testing$classe, prediction)
sum(testing$classe==prediction)/length(testing$classe)
```


We estimate less then 2% out of sample error

